---
title: "Intro to visual diff tools"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intro to visual diff tools}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(qctools)
```

```{r}
# # Helpful tools for QCing
# 
# When `logPending()` indicates a file is in need of QC but has previously had a 
# QC completed at an earlier revision, it is helpful to know what changed. This 
# can save QC efforts where only a minor change was made. 
# 
# `diffQced()` helps with this as it generates a visual diff in the Viewer pane 
# in RStudio. All deleted, added and modified lines of code are shown in the diff. 
# 
# When `diffQced()` is supplied a file name, it uses the QC log to identify the
# commit when the last QC was completed. The difference is then generated 
# using the version of the file at that commit versus the current file.
# 
# ```{r eval=FALSE}
# diffQced("script/data-assembly.R")
# ```
```

```{r}
# ```{r echo=FALSE, message=FALSE, results='asis'}
# curdir <- getwd()
# on.exit(setwd(curdir))
# setwd(repo)
# 
# version_qc <- qclog[qclog$file == "script/data-assembly.R", "commit"][2]
# commit_file_qc <- paste0(version_qc, ":", "script/data-assembly.R")
# x <- processx::run("git", c("cat-file", "blob", commit_file_qc),stdout = "data-assembly-1.R")
# 
# diffobj::diffFile(
#         "data-assembly-1.R",
#         "script/data-assembly.R",
#         color.mode = "rgb",
#         ignore.white.space = FALSE,
#         mode = "sidebyside",
#         tar.banner="QCed version",
#         cur.banner="Current",
#         format = "html",
#         style = list(html.output = "diff.w.style"),
#         interactive = F
#       )
# ```
```

