---
title: "Getting Started with mrgqc"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{getting-started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo=FALSE}
options(rmarkdown.html_vignette.check_title = FALSE)
```


# Introduction

This vignette takes the user through the basic functionality of the `mrgqc`
package. The user will gain experience with:

- creating and updating a QC log
- generating simple visual diffs to use during QC

# Setup

## Load libraries

```{r, message=FALSE}
library(mrgqc)
```

## Create demo repo

`demoRepo()` creates a temporary Git repo containing files with version history.
This repo already contains a QC log and partially completed QC for demonstration
purposes. The function returns the path to the repo.

```{r}
repo <- demoRepo()
print(repo)
```

# Using the QC log

If a repo does not contain a QC log, the first step would be to run `logCreate()`,
which will generate an empty one. As mentioned above, the demo repo already 
contains a QC log. The contents are shown below.

```{r, echo=FALSE, message=FALSE}
qclog <- utils::read.csv(file.path(repo, "QClog.csv"))
qclog
```

A few helpful definitions:

- `file`: Relative file path from the location of the QC log.
- `commit`: Commit hash of last modification to the file.
- `reviewer`: Reviewer of the file, given as the equivalent in R to `Sys.info()[["user"]]`.
- `datetime`: Time of the assignment or acceptance.

## logAssign

When a file is ready for QC, it should be assigned in the QC log. This
can be done using the `logAssign()` function, which will add a record to the QC
log.

Looking at the demo QC log, the first row is an example of a record that
`logAssign()` will generate.

```{r, echo=FALSE}
qclog[1, ]
```

Notice that `commit` is set to `Initial-Assignment` since the file has only been
added to the QC log and not actually QCed. Additionally, the reviewer is set to
"anyone". 

If we want to assign another file, such as `script/examp-yaml.yaml`, we can do 
the following:

```{r, eval=FALSE}
logAssign("script/examp-yaml.yaml")
```

## logAccept

After the reviewer completes their QC of a file, `logAccept()` should be used to
create a record of this. The commit at the time of QC is captured along
with the username of the reviewer. 

We can look at the QC history of `script/data-assembly.R` to demonstrate the
differences between `logAssign()` and `logAccept()`.

```{r, echo=FALSE}
qclog[qclog$file == "script/data-assembly.R", ]
```

Notice that the row created by `logAccept()` updated the `commit` value to the
commit hash of the most recent modification to the file when it was QCed. The 
reviewer was updated from "anyone" to the actual user who did the QC.

# logPending

`logPending()` is a helpful function for identifying files in need of QC. 
It will return all files that meet the following criteria:

- assigned with `logAssign()` but no completed QC
- modifications made since the last QC was done

Running `logPending()` on the demo repo will result with the following output:

```{r, echo=FALSE}
curdir <- getwd()
on.exit(setwd(curdir))
setwd(repo)
logPending()
```

Every row returned indicates a file in need of QC. Along with the relative 
path of the file, the author and most recent reviewer of the file is 
provided. If the reviewer is marked as "anyone" then the file has never 
been QCed before.

# Helpful tools for QCing

When `logPending()` indicates a file is in need of QC but has previously had a 
QC completed at an earlier revision, it is helpful to know what changed. This 
can save QC efforts where only a minor change was made. 

`diffQced()` helps with this as it generates a visual diff in the Viewer pane 
in RStudio. All deleted, added and modified lines of code are shown in the diff. 

When `diffQced()` is supplied a file name, it uses the QC log to identify the
commit when the last QC was completed. The difference is then generated 
using the version of the file at that commit versus the current file.

```{r eval=FALSE}
diffQced("script/data-assembly.R")
```

```{r echo=FALSE, message=FALSE, results='asis'}
curdir <- getwd()
on.exit(setwd(curdir))
setwd(repo)

version_qc <- qclog[qclog$file == "script/data-assembly.R", "commit"][2]
commit_file_qc <- paste0(version_qc, ":", "script/data-assembly.R")
x <- processx::run("git", c("cat-file", "blob", commit_file_qc),stdout = "data-assembly-1.R")

diffobj::diffFile(
        "data-assembly-1.R",
        "script/data-assembly.R",
        color.mode = "rgb",
        ignore.white.space = FALSE,
        mode = "sidebyside",
        tar.banner="QCed version",
        cur.banner="Current",
        format = "html",
        style = list(html.output = "diff.w.style"),
        interactive = F
      )
```

# QC Summary

`logSummary()` outputs all files in the QC log along with their QC status.

The QC status of a given file could be one of the following:

- `Assigned, needs QC`: file has been assigned in the QC log, but never has been QCed
- `Modified, needs QC`: file has been QCed previously, but has had modifications since
- `Fully QCed`: file has no QC needs currently. 

To see an example of a QC summary document, run the following locally:

```{r, eval=FALSE}
logSummary()
```

```{r, echo=FALSE}
curdir <- getwd()
on.exit(setwd(curdir))
setwd(repo)

logSummary()
```

