---
title: "Intro to QC log tools"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intro to QC log tools}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(qctools)
```

```{r}
# # Setup
# 
# ## Load libraries
# 
# ```{r, message=FALSE}
# library(qctools)
# ```
# 
# ## Create demo repo
# 
# `demoRepo()` creates a temporary Git repo containing files with version history.
# This repo already contains a QC log and partially completed QC for demonstration
# purposes. The function returns the path to the repo.
# 
# ```{r}
# repo <- demoRepo()
# print(repo)
# ```
# 
# # Using the QC log
# 
# If a repo does not contain a QC log, the first step would be to run `logCreate()`,
# which will generate an empty one. As mentioned above, the demo repo already 
# contains a QC log. The contents are shown below.
# 
# ```{r, echo=FALSE, message=FALSE}
# qclog <- utils::read.csv(file.path(repo, "QClog.csv"))
# qclog
# ```
# 
# A few helpful definitions:
# 
# - `file`: Relative file path from the location of the QC log.
# - `commit`: Commit hash of last modification to the file.
# - `reviewer`: Reviewer of the file, given as the equivalent in R to `Sys.info()[["user"]]`.
# - `datetime`: Time of the assignment or acceptance.
# 
# ## logAssign
# 
# When a file is ready for QC, it should be assigned in the QC log. This
# can be done using the `logAssign()` function, which will add a record to the QC
# log.
# 
# Looking at the demo QC log, the first row is an example of a record that
# `logAssign()` will generate.
# 
# ```{r, echo=FALSE}
# qclog[1, ]
# ```
# 
# Notice that `commit` is set to `Initial-Assignment` since the file has only been
# added to the QC log and not actually QCed. Additionally, the reviewer is set to
# "anyone". 
# 
# If we want to assign another file, such as `script/examp-yaml.yaml`, we can do 
# the following:
# 
# ```{r, eval=FALSE}
# logAssign("script/examp-yaml.yaml")
# ```
# 
# ## logAccept
# 
# After the reviewer completes their QC of a file, `logAccept()` should be used to
# create a record of this. The commit at the time of QC is captured along
# with the username of the reviewer. 
# 
# We can look at the QC history of `script/data-assembly.R` to demonstrate the
# differences between `logAssign()` and `logAccept()`.
# 
# ```{r, echo=FALSE}
# qclog[qclog$file == "script/data-assembly.R", ]
# ```
# 
# Notice that the row created by `logAccept()` updated the `commit` value to the
# commit hash of the most recent modification to the file when it was QCed. The 
# reviewer was updated from "anyone" to the actual user who did the QC.
# 
# # logPending
# 
# `logPending()` is a helpful function for identifying files in need of QC. 
# It will return all files that meet the following criteria:
# 
# - assigned with `logAssign()` but no completed QC
# - modifications made since the last QC was done
# 
# Running `logPending()` on the demo repo will result with the following output:
# 
# ```{r, echo=FALSE}
# with_demoRepo(
#   logPending()
# )
# ```
# 
# Every row returned indicates a file in need of QC. Along with the relative 
# path of the file, the author and most recent reviewer of the file is 
# provided. If the reviewer is marked as "anyone" then the file has never 
# been QCed before.
```

```{r}
# # QC Summary
# 
# `logSummary()` outputs all files in the QC log along with their QC status.
# 
# The QC status of a given file could be one of the following:
# 
# - `Assigned, needs QC`: file has been assigned in the QC log, but never has been QCed
# - `Modified, needs QC`: file has been QCed previously, but has had modifications since
# - `Fully QCed`: file has no QC needs currently. 
# 
# To see an example of a QC summary document, run the following locally:
# 
# ```{r, eval=FALSE}
# logSummary()
# ```
# 
# ```{r, echo=FALSE}
# curdir <- getwd()
# on.exit(setwd(curdir))
# setwd(repo)
# 
# logSummary()
# ```
```

